Investigating the change of Toronto crime rates from 2014-2023

### 2024-01-25 Output/paper.qmd
modified paper
test file added

---
title: "Investigating the change of Toronto crime rates from 2014-2023"
author: "Charles Cai"
thanks: "Code and data are available at: https://github.com/peachvegetable/STA_302_neighbourhood_crime-rate" 
date: "today"
date-format: "long" 
abstract: "This study presents an analysis of crime rates in the Wexford/Maryvale and Kensington-Chinatown neighborhoods over a ten-year period, revealing a notable increase in crime rates, especially in Kensington-Chinatown. The findings suggest that local socio-economic factors may significantly influence crime trends."
format: pdf
output: bookdown::pdf_document2
toc: true
number-sections: true
bibliography: reference.bib
---

@@

To examine the trends of crime in Toronto, I have sourced the "Neighbourhood Crime Rates" dataset from the Toronto Open Data Portal [@citeOpendataToronto]. This dataset, published by the City of Toronto, details crime statistics across various neighborhoods from 2014 to 2023. It has different crime types, including but not limited to assault, shooting, and theft, and presents these data points in the context of annual crime rates per 100,000 population.

>>>>

---
title: "Investigating the change of Toronto crime rates from 2014-2023"
author: "Charles Cai"
thanks: "Code and data are available at: https://github.com/peachvegetable/STA_302_neighbourhood_crime-rate" 
date: "today"
date-format: "long" 
abstract: "In this study, we analyzed crime data across two Toronto neighborhoods to identify trends from 2014 to 2023. Our findings indicate a significant rise in crime rates, with variation between the neighborhoods, particularly a sharp increase in Kensington-Chinatown. This research underscores the impact of local socio-economic factors on crime trends and highlights the necessity for community-specific strategies in crime prevention."
format: pdf
output: bookdown::pdf_document2
toc: true
number-sections: true
bibliography: reference.bib
---

@@

To examine the trends of crime in Toronto, I have sourced the "Neighbourhood Crime Rates" dataset from the Toronto Open Data Portal [@citeOpendataToronto]. This dataset, published by the City of Toronto [@citeCrimeRates], details crime statistics across various neighborhoods from 2014 to 2023. It has different crime types, including but not limited to assault, shooting, and theft, and presents these data points in the context of annual crime rates per 100,000 population.
